Towards Practical First-Order Model Counting

### 2025-01-16 doc/paper/paper.tex
Expand Section 2.3

\section{Preliminaries}\label{sec:preliminaries}
% TODO: focus more on current work
% TODO: Section 2 until 2.3 (Algebra) could be drastically shortened

@@

% TODO: this subsection could be expanded a little

We write $\expr{}$ to represent an arbitrary algebraic expression. It is
important to note that some terms have different meanings in algebra and
logic. In algebra, a \emph{constant} refers to a non-negative integer. Likewise,
a \emph{variable} can either be a parameter of a function or a variable
introduced through summation, such as $i$ in the expression
$\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is
$f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short), where $f$ represents an
$n$-ary function, and each $x_{i}$ represents a variable. An \emph{equation} is
$f(\mathbf{x}) = \expr{}$, with $f(\mathbf{x})$ representing a signature.

\begin{definition}[Base case]\label{def:basecase}
  Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
  or a variable (note that signatures are included in this definition). Then
  function call $f(\mathbf{y})$ is considered a \emph{base case} of
  $f(\mathbf{x})$ if $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a
  substitution that replaces one or more $x_{i}$ with a constant.
\end{definition}

>>>>

\section{Preliminaries}\label{sec:preliminaries}

@@

We write $\expr{}$ for an arbitrary algebraic expression. In the context of
algebra, a \emph{constant} is a non-negative integer. Likewise, a
\emph{variable} can either be a parameter of a function or a variable introduced
through summation, such as $i$ in the expression $\sum_{i=1}^{n} \expr$. A
\emph{function call} is $f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short),
where $f$ is an $n$-ary function, and each $x_{i}$ is an algebraic expression
consisting of variables and constants. A (function) \emph{signature} is function
call that contains only variables. An \emph{equation} is
$f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.

\begin{definition}[Base case]\label{def:basecase}
  Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
  or a variable. Then function call $f(\mathbf{y})$ is a \emph{base case} of
  $f(\mathbf{x})$ if $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a
  substitution that replaces one or more $x_{i}$ with a constant.
\end{definition}

\begin{example}
  In equation $f(m, n) = f(m-1, n) + nf(m-1, n-1)$, the only constant is $1$,
  and the variables are $m$ and $n$. The equation contains three function calls:
  one on the left-hand side, and two on the right-hand side. The function call
  on the left-hand side is a signature. Function calls such as $f(4, n)$,
  $f(m, 0)$, and $f(8, 1)$ are all considered base cases of $f(m, n)$ (only some
  of which are useful).
\end{example}
